An Extensible Approach to Verification of Embedded Systems

### 2014-05-03 tech-project/led_trans.tex
fuck

\section{Putting It All Together}

@@

Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right). The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{Leds\_Fac}. One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept. Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion (as illustrated after the assignment of \texttt{Toggling\_Capability}).

The \texttt{Leds\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.

>>>>

\section{EVALUATION}

@@

Depicted in figure \ref{fig:demo} is the C translation of \texttt{LED\_Telos\_Demo} consisting of a .h (left) and a portion of the .c (right). The \texttt{LED\_Telos\_Demo\_create()} function provides instantiations for all global facilities used in \texttt{LED\_Telos\_Demo}, including those for standard types such as integers, booleans, clock, as well as local facilities such as \texttt{LED\_Fac}. One additional thing to note within this create method is the temporary \texttt{\_\_arg\_0} integer variable -- representing the formal value \texttt{Strip\_Length} found within the concept. Note that this variable does not appear in the original source, but rather, is created by the translator in an effort to keep track of all literal argument values that require manual deletion (as illustrated after the assignment of \texttt{Toggling\_Capability}).

The \texttt{LED\_Fac} facility from the original source, represented here as a struct, uses a \texttt{core} field to access the methods and types found in the original concept, while any remaining fields correspond to enhancement pointers that serve a similar end -- in this case, providing access to the operations declared within  \texttt{Toggling\_Capability}.

### 2014-05-03 tech-project/specify_led.tex
fuck

end LEDs_Template;
\end{verbatim}

@@

    Facility Leds_Fac is LED_Template(3)
        externally realized by Std_Led_Realiz
     enhanced by Toggling_Capability
        realized by Toggling_Realiz;

@@

        (* Declare an LED strip *)
        Var L : Led;

@@

        Loop := True();
        While(Loop)
            changing Loop;
            maintaining ...
        do
            Leds_Fac.Toggle(L, I0);
            Std_Clock_Fac.Wait_500_Milli_Seconds();

            Leds_Fac.Toggle(L, I1);
            Std_Clock_Fac.Wait_500_Milli_Seconds();

            Leds_Fac.Toggle(L, I2);
            Std_Clock_Fac.Wait_500_Milli_Seconds();
        end;
    end Main;

>>>>

end LED_Template;
\end{verbatim}

@@

    Facility LED_Fac is LED_Template(3)
        externally realized by Std_LED_Realiz
     enhanced by Toggling_Capability
        realized by Toggling_Realiz;

@@

        (* Declare an LED strip *)
        Var L : LED;

@@

        Loop := True();
        While(Loop)
            changing Loop;
            maintaining ...
        do
            LED_Fac.Toggle(L, I0);
            Std_Clock_Fac.Wait_500_Milli_Seconds();

            LED_Fac.Toggle(L, I1);
            Std_Clock_Fac.Wait_500_Milli_Seconds();

            LED_Fac.Toggle(L, I2);
            Std_Clock_Fac.Wait_500_Milli_Seconds();
        end;
    end Main;

### 2014-05-03 tech-project/telos_platform.tex
changes since initial turn in
fixed minor bugs
fuck

The Telos mote \cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley. Its hardware includes an msp430 microcontroller containing 128 bytes of RAM and 10kB of programmable flash memory. A cc2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors. The mote also contains three onboard LEDs: One blue, one red, and one green.

%Additionally, the Telos board contains a total of three LEDs -- one red, one green, and one blue.

>>>>

The Telos mote\cite{polastre:2005} is a programmable, low power, wireless sensing device developed at UC Berkeley. Its hardware includes an MSP430-F1611 microcontroller containing 10kB of RAM and 48kB of programmable flash memory\cite{msp:2011}. A CC2420 radio stack provides the mote with broadcast and receiving capabilities, while optional sensing capabilities may be added in the form of light, humidity, and temperature sensors. The mote also contains three onboard LEDs: One blue, one red, and one green.
